%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Automatic data archiving and analysis system at Hefei Light Source (HLS-II)} % Organization/group
    {} % Location
    {Nov. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Local updated and deployed the Data archiving system based the EPICS Archiver Appliance (AA) at HLS-II;}
        \item {Developed the Auto Configurator using C and Python to realize the automatic configuration of the archiving parameters;}
        \item {Developed the Single-Page-Application (SPA) based on Vue.js and Highcharts to realize the visualization of historical and real-time data;}
        \item {Constructed the Hadoop big-data platform using Cloudera CDH;}
        \item {Developed the ETL program from AA and RDB Channel Archiver using Sqoop and Spark.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Interlocking and alarm system at HLS-II} % Organization/group
    {} % Location
    {May. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designed, developed and deployed the Configurable Software Interlock System for HLS-II}
        \item {Local updated and deployed the alarm system based on BEAST at HLS-II;}
        \item {Developed the alarm message push program via email \& SMS using Java;}
        \item {Upgraded the alarm system using Phoebus this year;}
        \item {Developing the new message push programs via WeChat using Python.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Control system design and construction for front-end devices of IRFEL} % Organization/group
    {} % Location
    {Sep. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed the IOC Applications for front-end devices of Infrared Free Electron Laser Light (IRFEL);}
        \item {Completed the controls of vacuum gauge, power supply, motor, etc;}
        \item {Designed and developed the operation interface using Phoebus and Display Builder;}
        \item {Constructed the server system based on VMware vSphere.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {High level control system for a coating equipment} % Organization/group
    {} % Location
    {Jun. 2015 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed the high level control system for a vacuum coating equipment using NI LabWindows/CVI;}
        \item {The control system includes the following functions: user rights division, rapid pumping and security protection for the vacuum system, flexible configuration for the complex process control, comprehensive process monitoring, comprehensive and detailed log system, an so on.;}
        \item {Developed the driver program for PCI-6221 card to realize wide range scanning of ion beam.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Research about the Redundant EPICS IOC and Industrial Real-time Ethernet} % Organization/group
    {} % Location
    {Feb. 2014 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designed and built a redundant platform in embedded Linux OS on both NI cRIO-9068 using the EPICS iocRedundancy toolkit;}
        \item {Designed and built a multilayer redundant control prototype system based on Profinet;}
        \item {Built the prototype system of openPOWERLINK and tested its real-time performance;}
        \item {Developed the EPICS driver to integrate openPOWERLINK into EPICS environment.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
