%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Journal articles} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {\textbf{Yifan Song}, Gongfa Liu. et.al, Automatic data archiving and visualization at HLS-II, Nuclear Science and Techniques, 2018, 29(9): 129}
       \item {Peng-quan Wen, \textbf{Yifan Song}, Bing Li, et al. Beam cleaning status in HLS-II storage ring. Nuclear Techniques, 2015,10:10-14 (in Chinese)}
       \item {Hao Kang, \textbf{Yifan Song}, Ke Xuan, Gong-fa Liu, Development of Control System for Vacuum Coating Equipment Based on Lab Windows/CVI, Vacuum, 2016 (in Chinese)}
       \item {Zi-yu Huang, \textbf{Yifan Song}, Gongfa Liu, et. al, Design of Interlock System of FELiChEM, Atomic Energy Science and Technology,2017,51(09):1724-1728 (in Chinese)}
      \end{cvitems}
    }

 %---------------------------------------------------------
\cventry
   {Conference articles} % Role
   {} % Title
   {} % Location
   {} % Date(s)
   {
   	\begin{cvitems} % Description(s)
   		\item {\textbf{Yifan Song}, Gongfa Liu, et.al, The Configurable Software Interlock System for HLS-II, Proceedings of IPAC2017, Copenhagen, Denmark}
   		\item {Shuang Xu, \textbf{Yifan Song}, et.al, Control system design for front end devices of IRFEL, Proceedings of IPAC2018, Vancouver, British Columbia, Canada, 2018}
   		\item{X.K. Sun, \textbf{Yifan. Song}, G. Liu, Distributed I/O System Based on Ethernet POWERLINK Under the EPICS Architecture,Vancouver, British Columbia, Canada, 2018}
   		\item{X.K. Sun, \textbf{Yifan Song}, Gongfa Liu, et. al, Design and Implementation of HLS-II Constant Temperature Cooling Water Control System, 2018(06):1139-1143 (in Chinese)}
   		\item {Zi-yu Huang,\textbf{Yifan Song}, et. al, A Redundant EPICS Control System Based on PROFINET, Proceedings of ICALEPCS2015, Melbourne, Australia, 2015}
   		\item {Zi-yu Huang, \textbf{Yifan Song}, et al. The Interlock System of FELiChEM, Proceedings of ICALEPCS2017, Barcelona, Spain, 2017}
   		\item {Zi-yu Huang, \textbf{Yifan Song}, G. Liu, EPICS Driver for Siemens CP1616 Communication Module, Vancouver, British Columbia, Canada, 2018}
   	\end{cvitems}
   }

%---------------------------------------------------------
  \cventry
    {Papers in Preparation} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Yifan Song, Gongfa Liu, Design and construction of the data warehouse based on Hadoop ecosystem at HLS-II}
        \item {Yifan Song, Gongfa Liu, Data Archiving and visualization of IRFEL}
      \end{cvitems}
    }
   
%---------------------------------------------------------
\end{cventries}
